This is an example of article title

### 2019-06-22 paper/paper.tex
chipsort github reference

This article presents {\tt ChipSort.jl}, a Julia module that implements SIMD and cache-aware sorting utilizing some of the techniques found in the literature. These include sorting and merging networks, the use of Combsort with Insertion sort finalization for medium sized arrays and of multi-way merging for large arrays. These techniques require not only tuning parameters such as vector and array sizes, but also generating specific code when implementing different size networks. \chipsort seeks to generate efficient custom code for each task, relying on Julia metaprogramming capabilities for that.

>>>>

This article presents {\tt ChipSort.jl}~\cite{nicolau_leal_werneck_2019_3228848}, a Julia module that implements SIMD and cache-aware sorting utilizing some of the techniques found in the literature. These include sorting and merging networks, the use of Combsort with Insertion sort finalization for medium sized arrays and of multi-way merging for large arrays. These techniques require not only tuning parameters such as vector and array sizes, but also generating specific code when implementing different size networks. \chipsort seeks to generate efficient custom code for each task, relying on Julia metaprogramming capabilities for that.
